Does Political Integration Make Cities Grow Faster?\\ Evidence From Dynastic Takeovers\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-03-02 paper/paper.tex
#2 add sketch to paper.tex
#2 sketch literature review

>>>>

\section{Literature review}

You should ultimately boil this down to one page. Identify strengths and weaknesses of related studies as they relate to my project. Contrast sharply. Highlight your contribution in the context of the rest. Give your best answer to the ``So What?'' question \textit{now}.

Begin with comments about the body of research as a whole. 
First of all, which field is your project located in? Or at the intersection of which fields?

Have there been many or few studies? Have they focused on similar questions, or different? Are they empirical or theoretical? Which kind of setting do they use? What kind of data do they use? Do they use fancy structural estimation of specific parameters in trade models? What about the others, that are more like yours? What are recent papers on? When was this topic popular?

Once you've set the stage, locate your project in it.
As of now, I think this project makes two main contributions: it shows the effects of integration in a historical context, and it's novel in using detailed regionally disaggregated panel data to attempt causal inference.

Then sharpen this localisation by comparing your project to salient papers from the different strands (thematic groups): first papers from a). then from b). then c). Explain merits and shortcomings of these papers in relation to the question. Explain how your study hopes to avoid flaws in their analyses, and, in stark terms, what it ultimately contributes. This concludes your lit review.

Strands of relevant literature (gradually copy these upward):

\subsection{State size and capacity}

Theory: \cite{as1997}

Historical evidence: \cite{cervellati2022}, \cite{koyama2017}, \cite{schoenholzer2018}, \cite{sng2014}

\subsection{Economic and political integration}

Theory: \cite{sapir2011}, \cite{asw2000}

Historical evidence: \cite{chilosi2013}, \cite{kindleberger1975}, \cite{wolf2009}, \cite{chen2004}

Effects: \cite{campos2019}

\subsection{HNEs in the HRE}

Papers using similar approaches: \cite{cantoni2011}

\subsection{Hereditary rule as a HNE}

Theory: \cite{besley2017}

Evidence: \cite{olken2005}, \cite{dube2020}, \cite{ottinger2022}
